---
title: "Admin tasks for the R courses"
---

```{r setup, include = FALSE}
targets::tar_config_set(
  store = here::here("_targets")
)
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = "#>"
)
library(tidyverse)
devtools::load_all()
precourse <- targets::tar_read(upcoming_precourse_survey)
```

These are the constants used for later functions.

```{r constants}
get_upcoming_course_dates("intro")[1]
course_date <- get_upcoming_course_dates("intro")[1]
course_level <- "intro" # list_course_ids()
course_name <- get_course_repo("intro")
org_gh_course_name <- glue::glue("{course_name}-{str_sub(course_date, end = 7)}")
```

```{r}
```

# Pre-course admin tasks

## Who didn't finish survey

Check those who didn't finish the survey yet. Do need the official list
to compare with, which can be deleted after the course.

```{r, eval=FALSE}
participants <- check_who_not_finish_survey(
  precourse,
  readr::read_csv(here::here("_ignore/official-participant-list.csv"))
)
nrow(participants)
View(participants)
```

Then need to send a reminder email to those who didn't complete the
survey or tasks yet.

<!-- TODO: Create function to create an email directly? https://gmailr.r-lib.org/ -->

```{r, eval=FALSE}
copy_emails_for_reminder(participants)
copy_reminder_email_text()
```

## Basic setup checks

Quickly check whether everyone has their setups done correctly.

```{r}
cat(check_setup(precourse), file = here::here("_ignore/setup.txt"))

if (get_upcoming_course() %in% c("inter", "advanced")) {
  cat(check_project_setup(precourse), file = here::here("_ignore/project-setup.txt"))
}
```

## Who has problems

List those who have problems and print their setups.

```{r}
problems <- precourse %>%
  check_precourse_problems()
```

### Description of the problems

```{r, results='asis'}
problems %>%
  check_problem_description() %>%
  cat()
```

### Setup of those with problems

<!-- TODO: Convert this in a way that it shows the setups and problems together? -->

```{r, results='asis'}
problems %>%
  check_setup() %>%
  cat()
```

### Setup of their projects

```{r, results='asis'}
if (course_level %in% c("inter", "advanced")) {
  problems %>%
    check_project_setup() %>%
    cat()
}
```

```{r}
precourse |>
  select(contains(c("full_name", "city"))) |>
  rename_with(~ c("name", "city")) |>
  pwalk(\(name, city) {
    Sys.sleep(runif(1, 0.5, 2.5))
    glue::glue("https://www.google.com/search?q={name}+{city}") |>
      # use `system("chromium-browser {ALL_WEBSITE_URLS})` to open all tabs at once
      browseURL()
  })
```

### Copy names to address in first day

Copy the names of those who have problems so I can paste it to something
like Telegram so I know who to seek out on the first day.

```{r, eval=FALSE}
problems %>%
  dplyr::pull(full_name) %>%
  copy_names_with_problems()
```

### Assigning members to groups

> Note: Intro course only.

Now we need to assign the learners to the groups.

```{r}
round_down_to_even <- function(x) {
  if ((x %% 2) == 1) {
    x <- x - 1
  }
  x
}

set.seed(12)
teams <- tibble(
  username = sample(usernames, length(usernames)),
  team_names = sample(praise::praise_parts$adjective, length(usernames) / 2) |>
    rep(times = 2) |>
    sample() |>
    str_c("-project")
)
count(teams, team_names)

if (course_level %in% c("intro", "adv")) {
  learners_in_groups <- assign_learners_to_groups(
    precourse,
    project_groups
  )
  count(learners_in_groups, team)
}
```

## Creating the GitHub org and groups

Follow the instructions on the [ghclass
vignette](https://rundel.github.io/ghclass/articles/ghclass.html).
First, you need to create the organization manually. Use the value in
here as the name:

```{r}
create_github_org <- function(id) {
  # course_date <- get_upcoming_course_dates(id)[1]
  course_date <- "2024-12-10"
  course_name <- get_course_repo(id)
  org_name <- glue::glue("{course_name}-{str_sub(course_date, end = 7)}")

  cli::cli_inform(c(
    "Create a GitHub organization with this name: {.val {org_name}} ",
    "*" = "Go to {.href https://github.com/account/organizations/new?plan=free}"
  ))

  continue <- yesno::yesno2("Have you finished creating the GitHub organization?")
  if (!continue) {
    cli::cli_abort("Organization wasn't created, stopping the function.")
  }

  ghclass::org_set_repo_permission(org_name, permission = "none")
  org_name
}
```

## Create projects to push to repos

Setting up the repos to have all the folders and files.

```{r, eval=FALSE}
clone_team_repos(org_gh_course_name)
```

```{r}
setup_team_projects <- function(
    data,
    organization) {
  checkmate::check_data_frame(data)
  checkmate::check_names(
    data,
    permutation.of = c("username", "team_names")
  )
  #
  # Invite to the org
  ghclass::org_invite(organization, data$username)
  #
  # Create the teams
  ghclass::team_create(
    organization,
    unique(data$team_names)
  )
  teams <- ghclass::org_teams(organization)
  #
  # Invite users to the team
  ghclass::team_invite(
    organization,
    data$username,
    data$team_names
  )

  gh_repos <- ghclass::repo_create(organization, data$team_names)
  gh_repos <- ghclass::org_repos(organization)
  ghclass::repo_add_team(sort(gh_repos), sort(unique(data$team_names)))
  setup_team_repos(organization)
}

setup_team_projects(teams, "r-cubed-advanced-2024-12")
```

```{r}
setup_instructor_team <- function(usernames, organization) {
  ghclass::org_invite(organization, usernames)
  ghclass::team_create(organization, "Helpers")
  ghclass::team_invite(
    organization,
    usernames,
    "Helpers"
  )

  ghclass::org_repos(organization) %>%
    purrr::walk(~ {
      ghclass::repo_team_permission(
        repo = .x,
        team = "Helpers",
        permission = "admin"
      )
    })
}

ghclass::org_teams("rostools")
ghclass::team_members("rostools", "Teaching")

setup_instructor_team(
  c("AndersAskeland", "Isabellvse", "lwjohnst86"),
  "r-cubed-advanced-2024-12"
)
```
