---
title: "Admin tasks for the R workshops"
---

```{r setup, include = FALSE}
targets::tar_config_set(
  store = "../_targets"
)
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = "#>"
)
library(tidyverse)
devtools::load_all()
preworkshop <- targets::tar_read(upcoming_preworkshop_survey)

# Constants
workshop_id <- "intro" # list_workshop_ids()
# TODO: Convert this to fetch from the workshop data files
instructors <- c("lwjohnst86", "AndersAskeland")
# Run `just create-group-names` first
team_names <- readr::read_lines(here::here("data-raw/group-names.txt"))
```

# Pre-workshop admin tasks

## Who didn't finish survey

Check those who didn't finish the survey yet. Do need the official list
to compare with, which can be deleted after the workshop.

```{r, eval=FALSE}
participants <- check_who_not_finish_survey(
  preworkshop,
  readr::read_csv(here::here("_ignore/official-participant-list.csv"))
)
nrow(participants)
View(participants)
```

Then need to send a reminder email to those who didn't complete the
survey or tasks yet.

<!-- TODO: Create function to create an email directly? https://gmailr.r-lib.org/ -->

```{r, eval=FALSE}
copy_emails_for_reminder(participants)
copy_reminder_email_text()
```

## Basic setup checks

Quickly check whether everyone has their setups done correctly.

```{r}
cat(check_setup(preworkshop), file = here::here("_ignore/setup.txt"))

if (get_upcoming_workshop() %in% c("inter", "adv")) {
  cat(check_project_setup(preworkshop), file = here::here("_ignore/project-setup.txt"))
}
```

## Who has problems

List those who have problems and print their setups.

```{r}
problems <- preworkshop |>
  check_preworkshop_problems()
```

### Description of the problems

```{r, results='asis'}
problems |>
  check_problem_description() |>
  cat()
```

### Setup of those with problems

<!-- TODO: Convert this in a way that it shows the setups and problems together? -->

```{r, results='asis'}
problems |>
  check_setup() |>
  cat()
```

### Setup of their projects

```{r, results='asis'}
if (workshop_id %in% c("inter", "adv")) {
  problems |>
    check_project_setup() |>
    cat()
}
```

```{r}
preworkshop |>
  select(contains(c("full_name", "city"))) |>
  rename_with(~ c("name", "city")) |>
  pwalk(\(name, city) {
    Sys.sleep(runif(1, 0.5, 2.5))
    glue::glue("https://www.google.com/search?q={name}+{city}") |>
      # use `system("chromium-browser {ALL_WEBSITE_URLS})` to open all tabs at once
      browseURL()
  })
```

### Copy names to address in first day

Copy the names of those who have problems so I can paste it to something
like Telegram so I know who to seek out on the first day.

```{r, eval=FALSE}
problems |>
  dplyr::pull(full_name) |>
  copy_names_with_problems()
```

### Assigning members to groups

Now we need to assign the learners to the groups.

```{r}
create_github_org(workshop_id)
```

```{r}
# TODO: Include this as part of create_teams?
org_name <- "r-cubed-intro-2026-02"
gh_team_names <- expand_grid(team_names, num = 1:2) |>
  glue::glue_data("{team_names}-{num}")
teams <- create_teams(preworkshop, gh_team_names)
setup_team_projects(teams, org_name)
create_gh_instructor_team(instructors, org_name)
```

```{r}
clone_team_repos("r-cubed-intro-2025-01")
pull_team_repos("r-cubed-intro-2025-01")
```
