---
title: "Advanced course admin tasks"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
devtools::load_all()
# This is needed to fix a clipr issue.
# Sys.setenv(DISPLAY = ":0")
```

# Pre-course admin tasks

Create the planning issue in the GitHub/GitLab repository.

```{r, eval=FALSE}
admin_create_planning_issue("r-cubed-intermediate", "2022-06-21")
```

## Fetch (and save) pre-survey responses

First thing, need to get the presurvey results.

```{r}
# TODO: How to get these authenticated? Run first and then build vignette?
googledrive::drive_auth()
googlesheets4::gs4_auth()
presurvey <- fetch_precourse_advanced()
```

## Who didn't finish survey

Check those who didn't finish the survey yet. Do need the official list
to compare with, which can be deleted after the course.

```{r, eval=FALSE}
participants <- check_who_not_finish_survey(
  presurvey, 
  readr::read_csv(here::here("_ignore/official-participant-list-emails-2022-12-07.csv"))
)
nrow(participants)
View(participants)
```

Then need to send a reminder email to those who didn't complete the
survey or tasks yet.

```{r, eval=FALSE}
copy_emails_for_reminder(participants)
copy_reminder_email_text()
```

## Basic setup checks

Quickly check whether everyone has their setups done correctly.

```{r, results='asis'}
cat(check_setup(presurvey))
```

```{r, results='asis'}
cat(check_project_setup(presurvey))
```

## Who has problems

List those who have problems and print their setups.

```{r, results='asis'}
problems <- presurvey %>% 
  check_precourse_problems() 

problems %>% 
  check_setup() %>% 
  cat()

problems %>% 
  check_project_setup() %>% 
  cat()
```

Copy the names of those who have problems so I can paste it to something
like Telegram so I know who to seek out on the first day.

```{r, eval=FALSE}
problems %>% 
  dplyr::pull(full_name) %>% 
  copy_names_with_problems()
```

## Create group names

Create some fun group names for the course. There is some manual action
here to select the names I think are interesting or funky.

```{r}
set.seed(124)
group_names <- create_group_names()
# 28/4
group_names_final <- group_names[c(55, 60, 30, 16, 27, 37, 26)]
```

Create PDF files of the group names, so we can print the files before
the first day and put one of them on each table.

```{r, eval=FALSE}
group_names_final %>% 
  group_names_to_one_pdf()
```

Then to create some HTML files (that I will print to file manually for
now) of strips of group names to cut out of on a paper.

```{r, eval=FALSE}
group_names_final %>% 
  group_names_as_strips_html(number_participants = 28)
```

## Invite to Slack group

```{r, eval=FALSE}
copy_emails_for_slack_invite(presurvey$email)
```

## Post course admin

Need to run these inside the project.

```{r, eval=FALSE}

```
