---
title: "Admin tasks for the R courses"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = "#>"
)
library(tidyverse)
library(ghclass)
devtools::load_all()
```

These are the constants used for later functions.

```{r constants}
course_date <- get_upcoming_course_dates("intro")[1]
course_level <- "intro" # list_course_ids()
course_name <- get_course_repo("intro")
org_gh_course_name <- glue::glue("{course_name}-{str_sub(course_date, end = 7)}")
```

The `{ghclass}` package requires a GitHub PAT in order to work.

```{r, eval=FALSE}
# Set GitHub PAT
# gitcreds::gitcreds_set()
ghclass::github_set_token(gitcreds::gitcreds_get(use_cache = FALSE)$password)
```

# Pre-course admin tasks

## Fetch (and save) pre-survey responses

Any admin task that requires participant information, we need to first
get that information from the precourse survey.

```{r}
# TODO: How to get these authenticated? Run first and then build vignette?
precourse <- get_precourse_survey(course_level) %>%
  filter(course_version == max(course_version))
```

## Who didn't finish survey

Check those who didn't finish the survey yet. Do need the official list
to compare with, which can be deleted after the course.

```{r, eval=FALSE}
participants <- check_who_not_finish_survey(
  precourse,
  readr::read_csv(here::here("_ignore/official-participant-list.csv"))
)
nrow(participants)
View(participants)
```

Then need to send a reminder email to those who didn't complete the
survey or tasks yet.

<!-- TODO: Create function to create an email directly? https://gmailr.r-lib.org/ -->

```{r, eval=FALSE}
copy_emails_for_reminder(participants)
copy_reminder_email_text()
```

## Basic setup checks

Quickly check whether everyone has their setups done correctly.

```{r, results='asis'}
cat(check_setup(precourse), file = here::here("_ignore/setup.txt"))
```

Then check their project setup

```{r, results='asis'}
if (course_level %in% c("inter", "advanced")) {
  cat(check_project_setup(precourse), file = here::here("_ignore/project-setup.txt"))
}
```

## Who has problems

List those who have problems and print their setups.

```{r, results='asis'}
problems <- precourse %>%
  check_precourse_problems()
```

### Description of the problems

```{r, results='asis'}
problems %>%
  check_problem_description() %>%
  cat()
```

### Setup of those with problems

<!-- TODO: Convert this in a way that it shows the setups and problems together? -->

```{r, results='asis'}
problems %>%
  check_setup() %>%
  cat()
```

### Setup of their projects

```{r, results='asis'}
if (course_level %in% c("inter", "advanced")) {
  problems %>%
    check_project_setup() %>%
    cat()
}
```

### Copy names to address in first day

Copy the names of those who have problems so I can paste it to something
like Telegram so I know who to seek out on the first day.

```{r, eval=FALSE}
problems %>%
  dplyr::pull(full_name) %>%
  copy_names_with_problems()
```

## Create group names

Create some fun group names for the course using the
[what3words](https://what3words.com/) API.

```{r}
number_groups <- ceiling(nrow(precourse) / 4)
group_names <- create_group_names(number_groups)
group_names
```

Create PDF files of the group names, so we can print the files before
the first day and put one of them on each table.

```{r, eval=FALSE, results='hide'}
group_names %>%
  group_names_to_one_pdf()
```

Then to create some HTML files (that I will print to file manually for
now) of strips of group names to cut out of on a paper.

```{r, eval=FALSE}
group_names %>%
  group_names_as_strips_html(number_participants = nrow(precourse))
```

### Assigning members to groups

> Note: Intro course only.

Now we need to assign the learners to the groups.

```{r}
round_down_to_even <- function(x) {
  if ((x %% 2) == 1){
    x <- x - 1
  }
  x
}
project_groups <- expand_grid(prefix = group_names, suffix = 1:2) |> 
  slice_head(n = round_down_to_even(nrow(precourse)) / 2) |> 
  glue::glue_data("{prefix}-{suffix}")
if (course_level %in% c("intro")) {
learners_in_groups <- assign_learners_to_groups(
  precourse,
  project_groups
)
count(learners_in_groups, team)
# View(learners_in_groups)

# Manually change if need be.
# learners_in_groups <- edit(learners_in_groups)
}
```

## Creating the GitHub org and groups

Follow the instructions on the [ghclass
vignette](https://rundel.github.io/ghclass/articles/ghclass.html).
First, you need to create the organization manually. Use the value in
here as the name:

```{r}
# Name for organization.
org_gh_course_name
```

Check details of the organization and set permissions:

```{r, eval=FALSE}
# org_set_repo_permission(org_gh_course_name, permission = "none")
org_sitrep(org_gh_course_name)
```

Invite participants onto GitHub:

```{r, eval=FALSE}
# org_invite(org_gh_course_name, precourse$github_username)
org_members(org_gh_course_name)
org_pending(org_gh_course_name)
```

Then we can create the teams based on the group names:

```{r, eval=FALSE}
team_create(org_gh_course_name, group_names_final)
org_teams(org_gh_course_name)
```

Then assign the people to the teams.

```{r, eval=FALSE}
# Use this to remove users from teams, if you mess up.
# bind_rows(
#   team_members(org_gh_course_name),
#   team_pending(org_gh_course_name)
# ) %>% 
#   distinct() %>% 
#   pwalk(\(team, user) team_remove(org = org_gh_course_name, user = user, team = team, team_type = "slug"))
team_invite(
  org_gh_course_name,
  learners_in_groups$github_username,
  learners_in_groups$team
)
```

We need to create repos for each team.

```{r, eval=FALSE}
gh_repos <- repo_create(org_gh_course_name, group_names_final)
repo_add_team(sort(gh_repos), sort(unique(learners_in_groups$team)))
```

Make a table for the planning issue to put the instructors in groups.
There might be some manual tinkering here.

```{r, eval=FALSE}
instructors <- tibble::tribble(
  ~name, ~github_username,
  "Luke", "lwjohnst86"
)
instructors_to_groups <- assign_instructors_to_groups(group_names_final, instructors$name)
```

Then take instructors and assigned teams and convert them into a
Markdown table to paste into the planning issue.

```{r, eval=FALSE}
instructors_to_groups %>%
  copy_instructors_to_groups_table(org_gh_course_name)
```

Create a Helpers only team, so the team can be assigned to all the
repos.

```{r, eval=FALSE}
org_invite(org_gh_course_name, instructors$github_username)
team_create(org_gh_course_name, "Helpers")
team_invite(
  org_gh_course_name,
  instructors$github_username,
  "Helpers"
)
```

Add helpers and instructors team to all repos and set permissions to
admin.

```{r, eval=FALSE}
org_repos(org_gh_course_name) %>% 
  walk(~ {
    repo_team_permission(
      repo = .x,
      team = "Helpers",
      permission = "admin"
    )
  })
```

## Invite to Slack group

```{r, eval=FALSE}
copy_emails_for_slack_invite(precourse$email)
```

## Create projects to push to repos

Setting up the repos to have all the folders and files.

```{r, eval=FALSE}
setup_team_repos(org_gh_course_name)
```

```{r, eval=FALSE}
clone_team_repos(org_gh_course_name)
```

## Post course admin

Need to run these inside the project.

```{r, eval=FALSE}
```
